---
title: "Plotly"
author: "Julian Jordi"
date: "October 30th, 2021"
output: html_document
---

## Plotly Exercise

In this assignment, we are going to re-draw a plot we produced in the course "Reproducible Research" of this Data Science Specialization.

The underlying data are the number of steps taken by time of day of a group of people. We load and preprocess it just as we did then.

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(lubridate)
activity = read_csv("data/activity.zip") %>% 
    group_by(interval) %>% 
    mutate(steps = ifelse(is.na(steps), mean(steps, na.rm = T), steps)) %>% 
    ungroup() %>% 
    mutate(weekday = wday(date, week_start = 1)) %>% 
    mutate(weekdayOrWeekend = ifelse(weekday <= 5, "weekday", "weekend")) %>% 
    mutate(weekdayOrWeekend = as.factor(weekdayOrWeekend))
```

```{r}
head(activity)
```

Just like before, we want to compare step activity during weekdays with the activity during weekends.

### Original plot with ggplot
The original plot looked as follows

```{r ggplot}
library(ggplot2, warn.conflicts = F)
ggplot <- activity %>% 
  group_by(interval, weekdayOrWeekend) %>% 
  summarise(steps = mean(steps)) %>% 
  ggplot(aes(x = interval, y = steps)) +
  geom_line() +
  facet_grid(rows = vars(weekdayOrWeekend)) +
  ylab("Number of steps") +
  xlab("Interval")

ggplot
```

### And now the Interactive Version with Plotly


```{r message=FALSE, warning=FALSE}
library(plotly)
```

```{r plotly}
plotly <- ggplotly(ggplot)
plotly
```

